### 2025-02-02 Paper/computers&geosiciences/CAGEO_LaTeXTemplate-main/main_document.tex
zsd

\author[0]{Ali Polat}[type=editor,
                        auid=000,bioid=1,orcid=0000-0002-9147-3633]
%\credit{ Author 1 contribution  }

@@

\begin{coverletter}

Dear Editors-in-Chief,
\newline

please find the enclosed manuscript "A Fast Method for Detecting Rock Blocks and Calculating Volumes and 3D Surface Areas" which i am submitting for exclusive consideration for publication in Computers \& Geosciences. I confirm that the submission follows all the requirements and includes all the items of the submission checklist.  
\newline

The manuscript presents a fast method for detecting rock blocks. Rock blocks were detected precisely using the U-Net network and transfer learning method. Train IoU, validation IoU, train F1-score and validation F1-score were calculated as 0.8497\%, 0.8461\%, 0.9186\%, and 0.9152\%, respectively. An algorithm was developed to calculate the volume and 3D surface area of rock blocks. The methods and algorithms used in the study can be used in many fields, such as engineering applications and geological-geomorphological studies.
\newline

I provide the source codes in a public repository with details listed in the section "Code availability".
\newline

Thanks for your consideration. 
\newline

Sincerely,
\newline

Ali Polat

Provincial Directorate of Disaster and Emergency, 58000, Sivas, Turkey ali.polat@afad.gov.tr
\newline

\textbf{Delete before submission:}

Please confirm that your submission follows all the requirements of the guidelines, including the submission checklist:

- Cover letter

- Highlights

- Authorship statement

- The manuscript must be single column and double spaced

- Reference must be in the author-date format

- Code availability section

*The manuscripts that do meet the requirement guidelines will be desk-rejected.

\end{coverletter}

\begin{highlights}
\item Rock blocks were detected precisely using the U-Net network and transfer learning method.
\item An algorithm was developed to calculate the volume and 3D surface area of rock blocks.
\item The approach can be readily adapted to other terrain-related segmentation problems, as well as to the calculation of volume and 3D surface areas.

\end{highlights}

@@

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV. An area was selected to create train images. Rock blocks within this area were labelled and mask images were created. Then segmentation process was completed by Python and necessary libraries, and the results were converted to the polygon as a vector file (Fig. \ref{fig:Figure3}). Moreover, the volumes and 3D surfaces of all the rocks were calculated.
This section includes an example of equation. 
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig3.jpg}
	\caption{ Workflow diagram}
	\label{fig:Figure3}
\end{figure}
\subsection{Data preparation}
In this study required data was collected by UAV. DJI phantom 3-Pro was used for image acquisition. First, the area to be flown is determined, then the necessary parameters for image acquisition are entered by the Pix4d Capture software. These parameters were chosen as follows.\\
– Flight altitude (altitude): 100 m.\\
– Flight speed (speed): Fast\\
– Camera angle (Angle): 70$^o$\\
– Overlap: 80\%\\

>>>>

\author[0]{Ali Polat}[orcid=0000-0002-9147-3633]
%\credit{ Author 1 contribution  }

@@

@@

\section{Methodology}
Creating the dataset is a big problem for classification or segmentation processes. In this study, Unmanned Air Vehicle (UAV) was used to collect data. An orthophoto image of the region was created from aerial photographs obtained by UAV. An area was selected to create train images. Rock blocks within this area were labelled and mask images were created. Then segmentation process was completed by Python and necessary libraries, and the results were converted to the polygon as a vector file. Moreover, the volumes and 3D surfaces of all the rocks were calculated (Fig. \ref{fig:Figure3}).

\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{figures/fig3.jpg}
	\caption{ Workflow diagram}
	\label{fig:Figure3}
\end{figure}
\subsection{Data preparation}
In this study required data was collected by UAV. DJI phantom 3-Pro was used for image acquisition. First, the area to be flown is determined, then the necessary parameters for image acquisition are entered by the Pix4d Capture software. These parameters were chosen as follows.\\
– Flight altitude (altitude): 100 m.\\
– Flight speed (speed): Fast\\
– Camera angle (Angle): 70$^o$\\
– Overlap: 80\%\\
